\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Project Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Future Work / Improvements}
While working on The Talking Mailbox project, several areas for potential improvements were identified 
that could enhance the functionality, reliability, and user experience of the system. These improvements 
include:
\begin{itemize}
    \item \textbf{Better tampering detection}: While the LDR and tilt sensor provide good and reliable tampering detection, they can be replaced with a single reed swich. This would reduce complexity and power consumption.
    \item \textbf{Improved housing}: Housing of the components can be combined with load cell platform for a better fit and protection of the components.
    \item \textbf{Additional information}: A camera can be added to capture images of the mail inside the box. This would provide visual confirmation of mail presence and enhance user experience. An LED can be used in conjunction 
                                            with the camera to provide illumination inside the mailbox even when closed.
    \item \textbf{Easier server access}: The server can be deployed on a local raspberry pi or similar device to allow for local access and control. This would eliminate the need for an external hosting service and provide more flexibility.
    \item \textbf{Tampering alert}: A buzzer can be added to the box, to alert surroundings when tampering is detected. This would enhance security and deter unauthorized access.
    \item \textbf{Enhanced power management}: A piezo can also be added to the lid to harvest energy from the opening and closing of the mailbox. This would extend battery life and reduce maintenance.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%