\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Project Summary}
Overall, the results validate the original design objectives of \project{} and demonstrate a clear improvement over existing smart mailbox solutions. By combining direct mail detection, low-power operation, and long-range wireless communication, the project delivers a practical and novel solution to the problem of unattended mailboxes. \project{} not only confirms the feasibility of weight-based mail detection but also establishes a foundation for future enhancements such as multi-mailbox management and tampering alerts.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Future Work / Improvements}
While working on The Talking Mailbox project, several areas for potential improvements were identified 
that could enhance the functionality, reliability, and user experience of the system. These improvements 
include:
\begin{itemize}
    \item \textbf{Better lid opening detection}: While the LDR and tilt sensor provide good and reliable detection of the lid opening, they can be replaced with a single reed switch. This would reduce complexity and power consumption.
    \item \textbf{Improved housing}: Housing of the components can be combined with load cell platform for a better fit and protection of the components.
    \item \textbf{Additional information}: A camera can be added to capture images of the mail inside the box. This would provide visual confirmation of mail presence and enhance user experience. An LED can be used in conjunction with the camera to provide illumination inside the mailbox even when closed.
    \item \textbf{Easier server access}: The server can be deployed on a local raspberry pi or similar device to allow for local access and control. This would eliminate the need for an external hosting service and provide more flexibility.
    \item \textbf{Tampering alert}: A buzzer can be added to sound an alarm when tampering is detected. This would enhance security.
    \item \textbf{Improved Battery Life}: Implementing low power design could improve battery life. This may include using a custom PCB with minimal components instead of development boards or integrating more low power components.
    \item \textbf{Energy harvesting}: A piezo-element can also be added to the lid to harvest energy from the opening and closing of the mailbox. This would extend battery life and reduce maintenance.
    \item \textbf{Expansion to multiple mailboxes}: The system can be expanded to support multiple mailboxes, serving multiple users from a single controller. With the existing device ID set-up in the code, this can be achieved simply by connecting multiple sensor configs to the MCU using multiplexers and expanding the payload by prefixing the unique device ID before the sensor data.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%